\ttitle

### 2013-07-08 Appendices/AppendixC.tex
WIP

>>>>

%---------------------------------------------
%---------------------------------------------
\clearpage
\section{Online novelty detection on temporal sequences, by Ma and Perkins}
Paper: \cite{ma2003online}.
This method uses support vectors for regression (in contrast with of classification).
The regression function, using a kernel function $K(x_i, x_j)$ can be written as:
%
\begin{equation}
  f(\vectorsym{x}) = \sum_{i=1}^l \theta_i K(\vectorsym{x}_i, \vectorsym{x}) + b,
\end{equation}
%
where $\theta_i$ is a coefficient resulting from the Lagrange multipliers of the original minimization problem.
A small fraction these of coefficients are non-zero, and the corresponding samples $\vectorsym{x}_i$ are the \emph{support vectors}.
The regression function $f(\vectorsym{x})$ is non-linear when a non-linear kernel is chosen.

The regression function is used to created a model of past observations.
A matching function is constructed which determines the matching value $V(t_0)$ of a new observations with the constructed model.
This matching value is the residual of the regression function at $t_0$.

The algorithm determines \emph{(novel) events}, \emph{occurrences} and \emph{surprises}.
\emph{Novel events} are defined as a series of observations for which the confidence value over the number of suprises (out-of-model observations) is high enough.
Events thus have a length; they are constructed of a sub-series of observations.

The papers presents an alternative implementation in order to handle fixed-resource environments and thus induce an online algorithm.
After $W$ observations have been observed and used for the trained model, the oldest observation is disregarded before the newly obtained observation is incorporated.

\emph{Note:} the Support Vector approach in this paper is used to select the observations to use in the regression model.
This differs from one-class applications of support vector machines.
The same authors have also presented a paper which does use one-class construction using support vector machines: \cite{ma2003time}.
